Initial Analysis

### 2019-11-29 Initial_Analysis.Rmd
Updates clean results function

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9) %>% 
    # Fix coding issues between MAC and Windows
    mutate(
    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
    Territory = gsub("R<e9>union (France)","Réunion",Territory),
    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
    )

@@

Catch_Country <- SAU_Catch_Data_b %>%
  group_by(eez_name) %>%
  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>%
  group_by(fishing_entity) %>%
  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
         Bins = cut(fishing_entity_catch,breaks = 4),
         Bins_Plot = cut(fishing_entity_catch,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(fishing_entity_catch > 0)

@@

save_plot(paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
          plot,
          base_height = 8,
          base_width = 8)

>>>>

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

    # Fix coding issues between MAC and Windows

  Clean_Results$Territory <- Clean_Results$Territory %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub(" R<e9>union (France)","Réunion",.)

  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub(" R<e9>union (France)","Réunion",.)

@@

Catch_Country <- SAU_Catch_Data %>%
  group_by(eez_name) %>%
  summarise(eez_catch = round(sum(total_catch,na.rm=T),2)) %>%
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>%
  group_by(fishing_entity) %>%
  summarise(fishing_entity_catch = sum(eez_catch,na.rm=T)/1000000) %>% # Million tones
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
         Bins = cut(fishing_entity_catch,breaks = 4),
         Bins_Plot = cut(fishing_entity_catch,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(fishing_entity_catch > 0)

@@

save_plot(
  # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
  "Plot.png",
  plot,
  base_height = 8,
  base_width = 8
)
